
---
title: "relationship between violent crime and police killings"
author: "Andoh and Bomi"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## data about Arrests in the US

We used data called "USArrests"" from R datasets to illustrate a variety of descriptive statistics.
followings are the tables of data.

```{r USArrests,include=TRUE}
USArrests
```

Followings are the means for each crime(Murder, Assault, UrbanPop, and Rape).
```{r, include=TRUE}
mean(USArrests$Murder)
mean(USArrests$Assault)
mean(USArrests$UrbanPop)
mean(USArrests$Rape)
```

The following figure is a plot of the number of Murder and the number of Assault.
Apparently, the two variables are correlated.
```{r,include=TRUE}
plot(USArrests$Murder, USArrests$Assault)
```

## Second data used is about Student Admissions at UC Berkeley - "UCBAdmissions"
we used data from R core datasets to illustrate a variaty of discriptive statistics.
followings are variables and levels of data.

```{r plots}
require(graphics)
apply(UCBAdmissions, c(1,2), sum)
mosaicplot(apply(UCBAdmissions, c(1,2), sum), main = "Student admissions at UC Berkeley")
```

