
---
title: "relationship between violent crime and police killings"
author: "Andoh and Bomi"
output:
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## First data about Arrests in the US

We used data called "USArrests"" from R datasets to illustrate a variety of descriptive statistics.
followings are the tables of data.

```{r USArrests,include=TRUE}
USArrests
```

Followings are the means for each crime(Murder, Assault, UrbanPop, and Rape) in all over the US.
```{r, include=TRUE}
mean(USArrests$Murder)
mean(USArrests$Assault)
mean(USArrests$UrbanPop)
mean(USArrests$Rape)
```

The following figure is a plot of the number of Murder and the number of Assault.
Apparently, the two variables are correlated.
```{r,include=TRUE}
plot(USArrests$Murder, USArrests$Assault)
```

Then, we try to predict the number of Murder by three variables; Assault, UrbanPop, and Rape.
```{r,include=TRUE}
reg1 <- lm(USArrests$Murder~USArrests$Assault + USArrests$UrbanPop + USArrests$Rape)
summary(reg1)
```

## Second data used is about Student Admissions at UC Berkeley - "UCBAdmissions"

we used data from R core datasets to illustrate a variaty of discriptive statistics.
followings are variables and levels of data.

There are cross-tabulating 4526 observations on 3 variables. The variables and their levels are as follows:

No	 Name	 Levels
1	 Admit	 Admitted, Rejected
2	 Gender	 Male, Female
3	 Dept	 A, B, C, D, E, F

```{r proportion table}
prop.table(UCBAdmissions)
```

```{r more readable format}
ftable(round(prop.table(UCBAdmissions), 3), row.vars="Dept", col.vars = c("Gender", "Admit"))
``` 

The following graph shows the aggregated Student admissions by comparing gender proportions over departments.
```{r plots}
require(graphics)
apply(UCBAdmissions, c(1,2), sum)
mosaicplot(apply(UCBAdmissions, c(1,2), sum), main = "Student admissions at UC Berkeley")
```
